Placing the spotted T Tauri star LkCa 4 on an HR diagram

### 2016-09-13 document/ms.tex
Includes Ian comments-- closes Issue #39

\begin{figure*}
 \centering
 \includegraphics[width=0.80\textwidth]{figures/spectral_postage_stamp_01}

 \includegraphics[width=0.80\textwidth]{figures/spectral_postage_stamp_02}

 \includegraphics[width=0.80\textwidth]{figures/spectral_postage_stamp_03} 
 \caption{Examples of spectral features in the observed IGRINS spectrum (thick gray line) that are present only in the hot (blue line) photosphere model (top panel), only in the cool (red line) photosphere model (middle panel), or in a mixture of hot and cool models (bottom panel).  The composite spectrum model (purple thin line) is consistent with the observed spectrum for a range of fill factors, with examples of the the median fill factor (middle panel spectrum) and $\pm2\sigma$ fill factors demarcated on the spectral postage stamps.  The right-most panels show the temperature-fill factor correlation for these spectral orders, with a straight-line fit (dashed black line) through all the samples.  The location of the samples used to make the synthetic spectra to the left are shown as solid black symbols.}
 \label{fig:specPostageStamp}
\end{figure*}

@@

\section{DISCUSSION or something}

@@

\subsection{Placing LkCa 4 on an HR Diagram}

@@

@@

We assumed that the \PHOENIX\ synthetic spectra are a good representation of the observed IGRINS spectrum of LkCa 4, a young star that possesses a strong magnetic field \citep{donati14}.  Cool sunspots are associated with locally heightened magnetic fields on the sun, so synthetic spectral models employing negligible magnetic fields will fail to fit magnetic sensitive features.  Magnetic fields will have two effects on the emergent spectrum- line broadening attributable to the Zeeman effect, and pressure broadening attributable to seeing deeper into deeper layers in the photosphere compared to the surrounding hotter photosphere.  The former effect will differentially impact lines with high magnetic sensitivity \citep[\emph{e.g.}][]{johnskrull99,deen13}.  The latter effect could masquerade as an apparent shift in surface gravity, as seen in mixture models of spotted stars with empirical templates composed of dwarfs and giants \citep{oneal96}.  Our tacit assumptions have been that these line-broadening effects are 1) relatively small compared to the gross appearance and disappearance of spectral lines at disparate temperatures, 2) there exist many orders and lines that are not affected at all, and 3) the Gaussian process noise model fosters some resilience against unknown residual spectrum correlations induced by such under-fitting.  We see tentative evidence for physics outside of the pre-computed model grids in the poor fits to the observed spectra in $K-$band.  Strong metal lines demonstrate large departures in their best fit $\Z$, as the na\:ive fitting strategy futilely attempts to minimize the residuals from Zeeman-broadened lines.  No pre-computed model grids including a range of surface magnetic fields are available at the wavelength range and spectral sampling needed to approach these questions within this spectral inference framework.

@@

The number of WTTS for which the areal filling factor of spots have been measured is relatively low.  V 410 Tau shows up to 41\% coverage of spots \citep{petrov94}.  Many more measurements exist for evolved giants and subgiants, with typical fill factors in the range 15$-$48\% \citep{berdyugina05}.  The prototypical BY Dra source is consistent with 60\% coverage fraction of moderately cool ($\Delta \teff =400$) penumbra \citep{chugainov76}.  By these comparisons, LkCa 4 seems on the high end of filling factor

>>>>

\begin{figure*}
 \centering
 \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_04} 
 \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_01} 
 \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_05} 
 \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_06} 
 \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_02} 
 \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_03} 
 \caption{Examples of spectral features in the observed IGRINS spectrum (thick gray line).  The composite spectrum model (purple thin line) is consistent with the observed spectrum for a range of fill factors, with examples of the the median fill factor (middle panel spectrum) and $\pm2\sigma$ fill factors demarcated on the spectral postage stamps.}
 \label{fig:specPostageStamp}
\end{figure*}

@@

\section{Placing LkCa 4 on the HR diagram}

@@

\subsection{Spot-corrected HR diagram placement}

@@

\section{Discussion}

@@

We assumed that the \PHOENIX\ synthetic spectra are a good representation of the observed IGRINS spectrum of LkCa 4, a young star that possesses a strong magnetic field \citep{donati14}.  Cool sunspots are associated with locally heightened magnetic fields on the sun, so synthetic spectral models employing negligible magnetic fields will fail to fit magnetic sensitive features.  Magnetic fields will have two effects on the emergent spectrum- line broadening attributable to the Zeeman effect, and pressure broadening attributable to seeing deeper into deeper layers in the photosphere compared to the surrounding hotter photosphere.  The former effect will differentially impact lines with high magnetic sensitivity \citep[\emph{e.g.}][]{johnskrull99,deen13}.  The latter effect could masquerade as an apparent shift in surface gravity, as seen in mixture models of spotted stars with empirical templates composed of dwarfs and giants \citep{oneal96}.  Our tacit assumptions have been that these line-broadening effects are 1) relatively small compared to the gross appearance and disappearance of spectral lines at disparate temperatures, 2) there exist many orders and lines that are not affected at all, and 3) the Gaussian process noise model fosters some resilience against unknown residual spectrum correlations induced by such under-fitting.  We see tentative evidence for physics outside of the pre-computed model grids in the poor fits to the observed spectra in $K-$band.  Strong metal lines demonstrate large departures in their best fit $\Z$, as the na\"{i}ve fitting strategy futilely attempts to minimize the residuals from Zeeman-broadened lines.  No pre-computed model grids including a range of surface magnetic fields are available at the wavelength range and spectral sampling needed to approach these questions within this spectral inference framework.

@@

The number of WTTS for which the areal filling factor of spots have been measured is relatively low.  V 410 Tau shows up to 41\% coverage of spots \citep{petrov94}.  Many more measurements exist for evolved giants and subgiants, with typical fill factors in the range 15$-$48\% \citep{berdyugina05}.  The prototypical BY Dra source is consistent with 60\% coverage fraction of moderately cool ($\Delta \teff =400$) penumbra \citep{chugainov76}.  By these comparisons, LkCa 4 seems on the high end of filling factor.
